---
title: "Evaluation for Performance (slips)"
author: "Jonas Hurst"
date: "2023-06-24"
output:
  pdf_document: default
  html_document: default
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("~/ma")
library(tidyverse)
library(bootES)
library(ggplot2)
library(gridExtra) # for putting two ggplots next two each other

set.seed(12345)

# import data
source("./get_data.R")
```



# All data

```{r, echo=FALSE}
hist(evaluation_data$slips, xlab="number of slips", ylab = "number of observations", main="Histogram for slips (all obs.)")

```


\newpage
# Performance (Slips)


```{r echo=FALSE}
ggplot(evaluation_data, aes(x = slips, fill = method)) +
  geom_bar(position = position_dodge2(preserve = "single"), col="black", aes(y=after_stat(prop)*100)) +
  scale_fill_manual(values = c("P2F" = p2f_color, "F2P" = f2p_color)) +
  scale_x_continuous(breaks=0:max(evaluation_data$slips))+
  labs(x="Effectiveness (slips / polygon)", y="% of polygons in method")+
  theme(legend.position = c(0.94, 0.92), legend.title = element_blank())
ggsave("./graphs/slips_histogram.png", width=12, height=8, units = "cm")


evaluation_data %>%
  group_by(method, slips) %>%
  summarise(count_slips = n(), .groups = "rowwise")

slips.summary <- evaluation_data %>%
  group_by(method)%>%
  summarize(n=n(), mean = mean(slips), median = median(slips), std.dv = sd(slips))

slips.summary

p2f.slips.bootES <- bootES(p2f$slips, R=5000)
f2p.slips.bootES <- bootES(f2p$slips, R=5000)

slip.bootESsummary <- data.frame(
  method = c("P2F", "F2P"),
  mean = c(p2f.slips.bootES$t0, f2p.slips.bootES$t0),
  mean.min = c(p2f.slips.bootES$bounds[1], f2p.slips.bootES$bounds[1]),
  mean.max = c(p2f.slips.bootES$bounds[2], f2p.slips.bootES$bounds[2])
)

```

\newpage
Mean with bootstrapped 95% CI

```{r, echo=FALSE, fig.asp=0.25}
ggplot(slip.bootESsummary,
       aes(y = method, x = mean, xmin = mean.min, xmax = mean.max, color = method)) +
  geom_pointrange() +
  scale_color_manual(values = c("P2F" = p2f_color, "F2P" = f2p_color)) +
  scale_fill_discrete(breaks = c("P2F", "F2P")) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank(), legend.position = "none")
ggsave("./graphs/slips_means_all.png", width=12, height=3, units = "cm")

p2f.slips.bootES
f2p.slips.bootES

bootES(evaluation_data, data.col="slips", group.col = "method", contrast=c("P2F", "F2P"), R=5000)

```


\newpage
## Comparison large/small beetween techniques
### Large polygons:

```{r, echo=FALSE}
p2f.slips.large.bootES <- bootES(p2f_large$slips, R=5000)
f2p.slips.large.bootES <- bootES(f2p_large$slips, R=5000)

slip.large.bootESSummary <- data.frame(
  method = c("P2F", "F2P"),
  mean = c(p2f.slips.large.bootES$t0, f2p.slips.large.bootES$t0),
  mean.min = c(p2f.slips.large.bootES$bounds[1], f2p.slips.large.bootES$bounds[1]),
  mean.max = c(p2f.slips.large.bootES$bounds[2], f2p.slips.large.bootES$bounds[2])
)
```


Mean with bootstrapped 95% CI

```{r, echo=FALSE, fig.asp=0.25}

ggplot(slip.large.bootESSummary, aes(y=method, x=mean, xmin = mean.min, xmax = mean.max, color=method))+
  geom_pointrange() +
  scale_color_manual(values = c("P2F" = p2f_color, "F2P" = f2p_color)) +
  scale_fill_manual(breaks = c("P2F", "F2P")) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank(), legend.position = "none")
ggsave("./graphs/slips_means_large.png", width=12, height=3, units = "cm")


p2f.slips.large.bootES
f2p.slips.large.bootES

bootES(evaluation_data_large, data.col="slips", group.col = "method", contrast=c("P2F", "F2P"), R=5000)
```



\newpage
### Small polygons:

```{r, echo=FALSE}
p2f.slips.small.bootES <- bootES(p2f_small$slips, R=5000)
f2p.slips.small.bootES <- bootES(f2p_small$slips, R=5000)

slip.small.bootESSummary <- data.frame(
  method = c("P2F", "F2P"),
  mean = c(p2f.slips.small.bootES$t0, f2p.slips.small.bootES$t0),
  mean.min = c(p2f.slips.small.bootES$bounds[1], f2p.slips.small.bootES$bounds[1]),
  mean.max = c(p2f.slips.small.bootES$bounds[2], f2p.slips.small.bootES$bounds[2])
)
```


Mean with bootstrapped 95% CI

```{r, echo=FALSE, fig.asp=0.25}

ggplot(slip.small.bootESSummary, aes(y=method, x=mean, xmin = mean.min, xmax = mean.max, color=method))+
  geom_pointrange() +
  scale_color_manual(values = c("P2F" = p2f_color, "F2P" = f2p_color)) +
  scale_fill_manual(breaks = c("P2F", "F2P")) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank(), legend.position = "none")
ggsave("./graphs/slips_means_small.png", width=12, height=3, units = "cm")


p2f.slips.small.bootES
f2p.slips.small.bootES

bootES(evaluation_data_small, data.col="slips", group.col = "method", contrast=c("P2F", "F2P"), R=5000)
```

\newpage
## Comparison large/small within technique
### P2F

```{r, echo=FALSE}
bootES(p2f, data.col="slips", group.col = "state_type", contrast=c("large", "small"), R=5000)
```


### F2P

```{r, echo=FALSE}
bootES(f2p, data.col="slips", group.col = "state_type", contrast=c("large", "small"), R=5000)
```


\newpage
### Learnability

Large polygons

```{r, echo=FALSE}

slips_by_polygon_large <- data.frame(matrix(ncol=5, nrow=0, dimnames=list(NULL, c("state_number", "method", "mean", "mean.min", "mean.max"))))

for (retrieve_nr in 1:3) {
  bootresult_large_p2f <- bootES(filter(p2f, state_number == retrieve_nr)$slips, R=5000)
  bootresult_large_f2p <- bootES(filter(f2p, state_number == retrieve_nr)$slips, R=5000)
  
  bootresult_large <- data.frame(
    state_number = c(retrieve_nr, retrieve_nr),
    method = c("P2F", "F2P"),
    mean = c(bootresult_large_p2f$t0, bootresult_large_f2p$t0),
    mean.min = c(bootresult_large_p2f$bounds[1], bootresult_large_f2p$bounds[1]),
    mean.max = c(bootresult_large_p2f$bounds[2], bootresult_large_f2p$bounds[2])
  )
  
  slips_by_polygon_large <- rbind(slips_by_polygon_large, bootresult_large)
}


scale_large_min <- min(slips_by_polygon_large$mean.min)
scale_large_max <- max(slips_by_polygon_large$mean.max)

ggplot(slips_by_polygon_large, aes(x=state_number, y=mean, ymin=mean.min, ymax=mean.max, color=method)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(width=0.2)) +
  scale_color_manual(values = c("P2F" = p2f_color, "F2P" = f2p_color))+
  #ylim(scale_large_min, scale_large_max) +
  scale_y_continuous(breaks=seq(floor(scale_large_min), ceiling(scale_large_max), by=1))+
  scale_x_continuous(breaks = 1:3) +
  xlab("State number") +
  ylab("Slips") +
  facet_grid(cols=vars(method)) +
  theme(legend.position = "none")
ggsave("./graphs/learn_slips_large.png", width=8, height=8, units = "cm")

```

Small polygons

```{r, echo=FALSE}

slips_by_polygon_small <- data.frame(matrix(ncol=5, nrow=0, dimnames=list(NULL, c("state_number", "method", "mean", "mean.min", "mean.max"))))

for (retrieve_nr in 4:6) {
  bootresult_small_p2f <- bootES(filter(p2f, state_number == retrieve_nr)$slips, R=5000)
  bootresult_small_f2p <- bootES(filter(f2p, state_number == retrieve_nr)$slips, R=5000)
  
  bootresult_small <- data.frame(
    state_number = c(retrieve_nr, retrieve_nr),
    method = c("P2F", "F2P"),
    mean = c(bootresult_small_p2f$t0, bootresult_small_f2p$t0),
    mean.min = c(bootresult_small_p2f$bounds[1], bootresult_small_f2p$bounds[1]),
    mean.max = c(bootresult_small_p2f$bounds[2], bootresult_small_f2p$bounds[2])
  )
  
  slips_by_polygon_small <- rbind(slips_by_polygon_small, bootresult_small)
}


scale_small_min <- min(slips_by_polygon_small$mean.min)
scale_small_max <- max(slips_by_polygon_small$mean.max)

ggplot(slips_by_polygon_small, aes(x=state_number, y=mean, ymin=mean.min, ymax=mean.max, color=method)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(width=0.2)) +
  scale_color_manual(values = c("P2F" = p2f_color, "F2P" = f2p_color))+
  ylim(scale_small_min, scale_small_max) +
  scale_x_continuous(breaks = 4:6) +
  xlab("State number") +
  ylab("Slips") +
  facet_grid(cols=vars(method)) +
  theme(legend.position = "none")
ggsave("./graphs/learn_slips_small.png", width=8, height=8, units = "cm")
```
Todo: Test this with Linear Mixed Model

\newpage
# Task failures

```{r, echo=FALSE}
failures <- evaluation_data %>%
  group_by(method, failure_meaning) %>%
  summarise(count = n(), .groups="keep") %>%
  pivot_wider(names_from = failure_meaning, values_from = count) %>%
  as.data.frame()

contingency_matrix <- matrix(
  c(failures$fail[1], failures$fail[2],
    failures$success[1], failures$success[2]), nrow = 2
  )

failures

fisher.test(contingency_matrix)
     
```

H0: columns are independent (= odds-ratio is 1)

p-Value > 0.05: not enough evidence to discard H0

no significant difference between columns

1 in inside 95% odds ratio interval -> does not differ significantly from 1